Variant detection model with improved robustness and accuracy for low-depth targeted next-generation sequencing data

### 2014-02-10 doc/2014bioinformatics_zhang/RVD3.tex
RVD3 test on HCC1187 data.

We propose a novel empirical Bayesian model to call variants in heterogeneous samples accurately. We present a Bayeisan sensitivity analysis of this hierarchical model to variations of the prior funstion.
Our model with information prior (log-normal prior) and non-information prior (Jeffreys prior) both performs a high accuracy (96\%) when applied to a known 0.1\% minor allele frequency within very low read depth (39).
Moreover, the model with Jeffreys prior presents much lower false discovery rate (FDR) to a known 0.1\% minor allele frequency event, compared with using improper prior.
For further validation, our statistical model was applied on the yeast sequence data which also shows a high specificity and sensitivity over a wide range of read depth.
This model is able o detect the emergence of a beneficial SNV earlier than was previously shown.

>>>>

We propose a novel empirical Bayesian model to call variants in heterogeneous samples accurately. We present a Bayeisan sensitivity analysis of this hierarchical model to variations of the prior function.
Our model with information prior (log-normal prior) and non-information prior (Jeffreys prior) both performs a high accuracy (96\%) when applied to a known 0.1\% minor allele frequency within very low read depth (39).
Moreover, the model with Jeffreys prior presents much lower false discovery rate (FDR) to a known 0.1\% minor allele frequency event, compared with using improper prior.
For further validation, our statistical model was applied on the yeast sequence data which also shows a high specificity and sensitivity over a wide range of read depth.
This model is able to detect the emergence of a beneficial SNV earlier than was previously shown.
